---
title: 'Assessment of the northern rock sole Stock in the Bering Sea and Aleutian Islands'
author:
  - name: 'Carey McGilliard'
    affiliations:
      - name: 'NOAA Fisheries Alaska Fisheries Science Center'
        address: '17109 Point Lena Loop Road'
        city: 'Juneau, AK'
        state: 'AK'
        postal-code: '99801'
date: today
keep-tex: true 
mainfont: 'Latin Modern Sans' 
cover: 
pdf-engine: lualatex
format: 
  pdf: 
    documentclass: article
    papersize: letter
    number-sections: true
    template-partials:
      - 'support_files/before-body.tex'
      - 'support_files/_titlepage.tex'
    include-in-header:
      - 'support_files/in-header.tex'
    toc: true
    sansfont: 'Latin Modern Sans'
    lof: true
    lot: true
    titlepage-geometry: 
      - top=2in
      - bottom=1in
      - right=1in
      - left=1in
output-file: 'northern_rock_sole_SAR_2026' 
params:
   office: 'AFSC'
   species: 'northern rock sole'
   spp_latin: ' Lepidopsetta polyxystra '
   region: 'Bering Sea and Aleutian Islands'
bibliography:  
  - asar_references.bib
csl: support_files/cjfas.csl
---
\printnoidxglossaries 

```{r} 
#| label: 'R_parameters'
#| echo: false 
#| warnings: false 
#| eval: true
# Parameters 
spp <- params$species 
SPP <- params$species 
species <- params$species 
spp_latin <- params$spp_latin 
office <- params$office
region <- params$region
``` 

```{r} 
#| label: 'preamble'
#| warning: false 
#| eval: false 
#| include: false
# load converted output from stockplotr::convert_output() 

# Call reference points and quantities below 
output <- out_new |> 
  dplyr::mutate(estimate = as.numeric(estimate), 
    uncertainty = as.numeric(uncertainty)) 
source("preamble.R") 
# Available quantities
start_year
end_year
Fend # terminal fishing mortality
Ftarg # fishing mortality at msy
F_Ftarg # Terminal year F respective to F target
Bend # terminal year biomass
Btarg # target biomass (msy)
total_catch # total catch in the last year
total_landings # total landings in the last year
SBend # spawning biomass in the last year
M # overall natural mortality or at age
Bmsy # target spawning biomass(msy)
h # steepness
R0 # recruitment

``` 

{{< pagebreak >}}

## Disclaimer {.unnumbered .unlisted}

These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited or reproduced. They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce.

{{< pagebreak >}} 

Please cite this publication as: 

McGilliard, C. 2026. Assessment of the northern rock sole Stock in the Bering Sea and Aleutian Islands. North Pacific Fishery Management Council, Anchorage, AK. Available from https://www.npfmc.org/library/safe-reports/ \pageref*{LastPage}{} pp.

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'summary'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01_summary.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'main-table'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01a_main-table.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'apportionment'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01b_apportionment.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'plan-team'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01c_plan-team.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'responses'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('02_responses.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'introduction'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('03_introduction.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'fishery'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04_fishery.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'data'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('05_data.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'model'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('06_model.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'results'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('07_results.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'abc'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('08_abc.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'ecosystem'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('09_ecosystem.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'gaps'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('10_gaps.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'tables'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('11_tables.qmd', quiet = TRUE)
cat(a, sep = '\n')
# Force LaTeX to render all floating tables before moving to the next section
cat('\n\\clearpage\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'figures'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('12_figures.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'references'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('13_references.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'appendix'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('14_appendix.qmd', quiet = TRUE)
cat(a, sep = '\n')
```
